### 2022-10-26 manuscript.tex
Adding parenthesis to a link [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3f5fcbe49678055053a9a9df3dabe7aed164fdd3.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/3f5fcbe49678055053a9a9df3dabe7aed164fdd3/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/3332243977

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/891e1faad1b05462ff855da04e5af9c7a676855d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/891e1faad1b05462ff855da04e5af9c7a676855d}{SORTEE-Github-Hackathon/manuscript@891e1fa}
on October 26, 2022.

@@

With over 83 million registered users as of 2022, GitHub \url{https://github.com} is the most widely-used web platform for collaborating on computer code (\protect\hyperlink{ref-nwCtHDCn}{\emph{Build Software Better, Together}, n.d.}).
GitHub provides a simple but powerful web interface that allows users to participate in projects by contributing, modifying and discussing existing code, reporting bugs, discovering code and data, and publishing new code.
Through version control, users have a detailed, chronological record of the files and directories stored in their repositories (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}) (see \protect\hyperlink{definitions}{Box 1}).
This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.}, via email), a process that can become challenging and time-consuming in long-term and collaborative projects (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
Through its combination of version control and collaborative features, GitHub facilitates open-source code alongside collaborative development (\protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}).

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3f5fcbe49678055053a9a9df3dabe7aed164fdd3/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3f5fcbe49678055053a9a9df3dabe7aed164fdd3}{SORTEE-Github-Hackathon/manuscript@3f5fcbe}
on October 26, 2022.

@@

With over 83 million registered users as of 2022, GitHub (\url{https://github.com}) is the most widely-used web platform for collaborating on computer code (\protect\hyperlink{ref-nwCtHDCn}{\emph{Build Software Better, Together}, n.d.}).
GitHub provides a simple but powerful web interface that allows users to participate in projects by contributing, modifying and discussing existing code, reporting bugs, discovering code and data, and publishing new code.
Through version control, users have a detailed, chronological record of the files and directories stored in their repositories (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}) (see \protect\hyperlink{definitions}{Box 1}).
This workflow provides a strong and clear advantage over sending files back-and-forth (\emph{e.g.}, via email), a process that can become challenging and time-consuming in long-term and collaborative projects (\protect\hyperlink{ref-4ny1onB0}{Ram, 2013}).
Through its combination of version control and collaborative features, GitHub facilitates open-source code alongside collaborative development (\protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}).
